---
title: "DSS Analysis"
output: html_document
date: "2025-09-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Load libraries
```{r}
library(ggplot2)
library(devtools)
library(dplyr)
library(annotate)
library(stringr)
library(preprocessCore)
library(measures)
library(remotes)
library(mlr)
library(mlr3filters)
library(Metrics)
library(MLmetrics)
library(reshape2)
library(Rmisc)
library(survival)
library(survminer)
library(pheatmap)
library(RColorBrewer)
library(forestplot)
library(survey)
library(gtsummary)
library(flextable)
library(openxlsx)
library(tidyr)
library(rstatix)
library(ggpubr)
library(ggmosaic)
```

#Load the finalized and compiled DSS DFS data 
```{r}
urlfile<-'https://raw.githubusercontent.com/skubleny/DFS-GC-Subtype-Analysis/main/Data/dfsdss_data.csv'
DFSDSS_data <-read.csv(urlfile, row.names = 1, stringsAsFactors = TRUE)

```


#Supplementary table 2
Supplement table of the demographics for the cohort with the DFS and DSS NAs removed
```{r}

############
############
####DSS#####
############
############
############
############################
data_sub = DFSDSS_data %>% filter(!(is.na(DSS_status) | is.na(DSS_time)))

tb_overall = tbl_summary(data_sub,
             percent = "column", 
             include=c("age","stage", "sex", "TCGA_subtype", "ACRG_subtype", "TME_subtype_cal", "study", "tumour_location_coarse", "chemotherapy", "radiation", "chemorads")) %>% 
   remove_row_type(variables = everything(),type = "missing") %>% 
   add_n(col_label="**n/N (Missing %)**", statistic= "{N_nonmiss} / {N_obs} ({p_miss}%)", add_footnote = "Percent") 
 
tb_overall_flex = as_flex_table(
  tb_overall,
  include = everything(),
  return_calls = FALSE,
  strip_md_bold = TRUE
)
 
save_as_docx("tb_overall" = tb_overall_flex,path = "DSS_cohort_supplement.docx")

table2 <-
  tbl_summary(
    data_sub,
    include = c("age","stage", "sex", "TCGA_subtype", "ACRG_subtype", "TME_subtype_cal", "study", "tumour_location_coarse", "chemotherapy", "radiation", "chemorads"),
    by = study, # split table by group
    missing = "no" # don't list missing data separately
  ) %>%
  add_p()


table2 = as_flex_table(
  table2,
  include = everything(),
  return_calls = FALSE,
  strip_md_bold = TRUE
)
save_as_docx("table2" = table2,path = "DSS_cohort_supplement_section2.docx")

```


#Median follow up time
```{r}
#DSS median follow up 
check = DFSDSS_data
check$DSS_status = ifelse(check$DSS_status == 1, 0, 1)
fit <- survfit(Surv(DSS_time, DSS_status==0) ~ 1, data = check)
surv_median(fit)

fit <- survfit(Surv(DSS_time, DSS_status==0) ~ 1 + study, data = check)
surv_median(fit)
```

#Univariate DSS continuous variable hazard ratio plots 
```{r}
#TCGA
multivariate_cox = coxph(Surv(DSS_time, DSS_status) ~ STAD_EBV + STAD_MSI + STAD_GS + STAD_CIN , data = DFSDSS_data)
summary(multivariate_cox)

broom <- broom::tidy(multivariate_cox, exponentiate = TRUE, conf.int = TRUE)
broom$compiled = sprintf("%.2f (%.2f, %.2f)", broom$estimate, broom$conf.low, broom$conf.high)
write.csv(broom, "broom_tcga_survival_DSS.csv")

multivariate_cox_table = tbl_regression(multivariate_cox, exponentiate = TRUE)

multivariate_cox_table = as_flex_table(
  multivariate_cox_table,
  include = everything(),
  return_calls = FALSE)
 
flextable::save_as_docx("multivariate_cox_table" = multivariate_cox_table,path = "univariate_cox_tcga_DSS.docx")

#ACRG
multivariate_cox = coxph(Surv(DSS_time, DSS_status) ~ MSS_TP53neg + MSS_TP53pos + MSI + EMT, data = DFSDSS_data)
summary(multivariate_cox)

broom <- broom::tidy(multivariate_cox, exponentiate = TRUE, conf.int = TRUE)
broom$compiled = sprintf("%.2f (%.2f, %.2f)", broom$estimate, broom$conf.low, broom$conf.high)
write.csv(broom, "broom_acrg_survival_DSS.csv")

multivariate_cox_table = tbl_regression(multivariate_cox, exponentiate = TRUE)

multivariate_cox_table = as_flex_table(
  multivariate_cox_table,
  include = everything(),
  return_calls = FALSE)
 
flextable::save_as_docx("multivariate_cox_table" = multivariate_cox_table,path = "univariate_cox_acrg_DSS.docx")


#TME
multivariate_cox = coxph(Surv(DSS_time, DSS_status) ~ High_cal + Low_cal, data = DFSDSS_data)
summary(multivariate_cox)

broom <- broom::tidy(multivariate_cox, exponentiate = TRUE, conf.int = TRUE)
broom$compiled = sprintf("%.2f (%.2f, %.2f)", broom$estimate, broom$conf.low, broom$conf.high)
write.csv(broom, "broom_tme_survival_DSS.csv")

multivariate_cox_table = tbl_regression(multivariate_cox, exponentiate = TRUE)

multivariate_cox_table = as_flex_table(
  multivariate_cox_table,
  include = everything(),
  return_calls = FALSE)
 
flextable::save_as_docx("multivariate_cox_table" = multivariate_cox_table,path = "univariate_cox_tme_DSS.docx")

```
#Univariate cox forest tcga
```{r}


multivariate_cox_discrete = coxph(Surv(DSS_time, DSS_status) ~ TCGA_subtype , data = DFSDSS_data)
summary(multivariate_cox_discrete)

wald_mutli = car::Anova(multivariate_cox_discrete)

#######################NEW Sep 4, 2025 without global wald###########################
####################################################################
####################################################################

#Imported table text                 
table_text <- read.delim("~/Documents/R projects/Integrated Gastric Cancer Analyses/tcga_survival_DSS_forest.txt", header=FALSE)
table_text = as.matrix(table_text)
table_text = na_if(table_text, '')
table_text = table_text[,-3]

table_data <- read.delim("~/Documents/R projects/Integrated Gastric Cancer Analyses/tcga_survival_DSS_forest.txt")
table_data = table_data[,-3]


subgps <- c(3,4,5,6)
table_text[subgps] <- paste("  ",table_text[subgps]) 

table_text = as.matrix(table_text[,-c(3:5)])
table_text_list = list(list(), list())
        table_text_list[[1]] <- table_text[,1]
        table_text_list[[2]] <- table_text[,2]
        table_text_list[[1]][1] <- list(expression(bold("Variable")))
        table_text_list[[2]][1] <- list(expression(bold("HR (95% CI)")))
        table_text_list[[1]][2] <- list(expression(bold("TCGA Subtype")))
      

forestplot_final = forestplot(table_text_list, mean = cbind(c(NA, table_data$hazard)),lower = cbind(c(NA, table_data$lower)) ,upper = cbind(c(NA, table_data$upper)), 
           new_page = TRUE,
           zero = 1,
           colgap = unit(2,"mm"),
           lineheight = unit(5.5,"mm"),
           line.margin = unit(0.1,"mm"),
           graphwidth = unit(38,"mm"),
           clip = c(0.20, 2) ,
           boxsize = 0.6,
           align = c("l", "l", "l"),
           grid = structure((1), gp = gpar(col = "black", lty = 2, lwd = 1)),
           xlog=TRUE,
           vertices = TRUE,
           lwd.ci = 2,
           ci.vertices.height = 0.25,
           xticks = c(0.2, 0.50, 1,2), 
           col = fpColors(box = "seagreen", lines = "seagreen"),
           txt_gp = fpTxtGp(label = gpar(ps= 7, align ="left", cex=1.15),
                            ticks = gpar(ps= 7, cex = 1.15),
                            xlab = gpar(ps= 7, cex = 1.05)),
           hrzl_lines = list("2" = gpar(lwd = 1, columns = 1:3, col = "black"), 
                            "7" = gpar(lwd = 1, columns = 1:2, col = "black")),
           xlab  = "Hazard Ratio (95% CI)")
forestplot_final

svg("forestplot_tcga_DSS_nowald_sep2025.svg", width=5, height=2.5)
forestplot_final
dev.off()

```
#Univariate cox forest acrg
```{r}


multivariate_cox_discrete = coxph(Surv(DSS_time, DSS_status) ~ ACRG_subtype , data = DFSDSS_data)
summary(multivariate_cox_discrete)

wald_mutli = car::Anova(multivariate_cox_discrete)

#######################NEW MARCH 13, 2024 without global wald###########################
####################################################################
####################################################################

#Imported table text                 
table_text <- read.delim("~/Documents/R projects/Integrated Gastric Cancer Analyses/acrg_survival_DSS_forest.txt", header=FALSE)
table_text = as.matrix(table_text)
table_text = na_if(table_text, '')
table_text = table_text[,-3]

table_data <- read.delim("~/Documents/R projects/Integrated Gastric Cancer Analyses/acrg_survival_DSS_forest.txt")
table_data = table_data[,-3]


subgps <- c(3,4,5,6)
table_text[subgps] <- paste("  ",table_text[subgps]) 

table_text = as.matrix(table_text[,-c(3:5)])
table_text_list = list(list(), list())
        table_text_list[[1]] <- table_text[,1]
        table_text_list[[2]] <- table_text[,2]
        table_text_list[[1]][1] <- list(expression(bold("Variable")))
        table_text_list[[2]][1] <- list(expression(bold("HR (95% CI)")))
        table_text_list[[1]][2] <- list(expression(bold("ACRG Subtype")))
        


forestplot_final = forestplot(table_text_list, mean = cbind(c(NA, table_data$hazard)),lower = cbind(c(NA, table_data$lower)) ,upper = cbind(c(NA, table_data$upper)), 
           new_page = TRUE,
           zero = 1,
           colgap = unit(2,"mm"),
           lineheight = unit(5.5,"mm"),
           line.margin = unit(0.1,"mm"),
           graphwidth = unit(40,"mm"),
           clip = c(0.20, 2) ,
           boxsize = 0.6,
           align = c("l", "l", "l"),
           grid = structure((1), gp = gpar(col = "black", lty = 2, lwd = 1)),
           xlog=TRUE,
           vertices = TRUE,
           lwd.ci = 2,
           ci.vertices.height = 0.25,
           xticks = c(0.2, 0.50, 1,2), 
           col = fpColors(box = "seagreen", lines = "seagreen"),
           txt_gp = fpTxtGp(label = gpar(ps= 7, align ="left", cex=1.15),
                            ticks = gpar(ps= 7, cex = 1.15),
                            xlab = gpar(ps= 7, cex = 1.05)),
           hrzl_lines = list("2" = gpar(lwd = 1, columns = 1:3, col = "black"), 
                            "7" = gpar(lwd = 1, columns = 1:2, col = "black")),
           xlab  = "Hazard Ratio (95% CI)")
forestplot_final

svg("forestplot_acrg_DSS_nowald_sep2025.svg", width=5.1, height=2.5)
forestplot_final
dev.off()

```
#Univariate cox forest tme
```{r}


multivariate_cox_discrete = coxph(Surv(DSS_time, DSS_status) ~ High_cal , data = DFSDSS_data)
summary(multivariate_cox_discrete)

wald_mutli = car::Anova(multivariate_cox_discrete)


#######################NEW MARCH 13, 2024 without global wald###########################
####################################################################
####################################################################

#Imported table text                 
table_text <- read.delim("~/Documents/R projects/Integrated Gastric Cancer Analyses/tme_survival_DSS_forest.txt", header=FALSE)
table_text = as.matrix(table_text)
table_text = na_if(table_text, '')
table_text = table_text[,-3]

table_data <- read.delim("~/Documents/R projects/Integrated Gastric Cancer Analyses/tme_survival_DSS_forest.txt")
table_data = table_data[,-3]


subgps <- c(3,4,5,6)
table_text[subgps] <- paste("  ",table_text[subgps]) 

table_text = as.matrix(table_text[,-c(3:5)])
table_text_list = list(list(), list())
        table_text_list[[1]] <- table_text[,1]
        table_text_list[[2]] <- table_text[,2]
        table_text_list[[1]][1] <- list(expression(bold("Variable")))
        table_text_list[[2]][1] <- list(expression(bold("HR (95% CI)")))
        table_text_list[[1]][2] <- list(expression(bold("TME Subtype")))
        


forestplot_final = forestplot(table_text_list, mean = cbind(c(NA, table_data$hazard)),lower = cbind(c(NA, table_data$lower)) ,upper = cbind(c(NA, table_data$upper)), 
           new_page = TRUE,
           zero = 1,
           colgap = unit(2,"mm"),
           lineheight = unit(5.5,"mm"),
           line.margin = unit(0.1,"mm"),
           graphwidth = unit(40,"mm"),
           clip = c(0.20, 2),
           boxsize = 0.8,
           align = c("l", "l", "l"),
           grid = structure((1), gp = gpar(col = "black", lty = 2, lwd = 1)),
           xlog=TRUE,
           vertices = TRUE,
           lwd.ci = 2,
           ci.vertices.height = 0.25,
           xticks = c(0.1, 0.50, 1,2), 
           col = fpColors(box = "seagreen", lines = "seagreen"),
           txt_gp = fpTxtGp(label = gpar(ps= 7, align ="left", cex=1.15),
                            ticks = gpar(ps= 7, cex = 1.15),
                            xlab = gpar(ps= 7, cex = 1.05)),
           hrzl_lines = list("2" = gpar(lwd = 1, columns = 1:3, col = "black"), 
                            "5" = gpar(lwd = 1, columns = 1:2, col = "black")),
           xlab  = "Hazard Ratio (95% CI)")
forestplot_final

svg("forestplot_tme_DSS_nowald_Sep2025.svg", width=5, height=2.25)
forestplot_final
dev.off()

```
#Univariate subtype DSS survival (discrete with risk table)
```{r}
#TCGA cox
TCGA_cox_rfs = coxph(Surv(DSS_time, DSS_status) ~ TCGA_subtype, data = DFSDSS_data)
summary(TCGA_cox_rfs)
summary(survfit(Surv(DSS_time, DSS_status) ~ TCGA_subtype, data = DFSDSS_data), times = 60)
pairwise_survdiff(Surv(DSS_time, DSS_status) ~ TCGA_subtype, data = DFSDSS_data)

tcga_km_DSS_risk = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TCGA_subtype, data = DFSDSS_data), 
           risk.table=TRUE, 
           risk.table.y.text = FALSE, 
           pval= "Logrank test \n p < 0.05", 
           pval.coord = c(80, 0.95),
           palette = c("#F39B7FFF", "#91D1C2FF", "#4DBBD5FF", "#E64B35FF"),
           risk.table.y.text.col = TRUE,
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS probability",
           legend = c(0.25,0.24),
           title = "TCGA Kaplan-Meier",
           legend.title = "TCGA Subtype",
           legend.labs=c("CIN", "EBV", "GS", "MSI"),
           font.legend = c(12, "plain", "black"),
           font.main = c(16, "plain", "black"),
           font.x = c(16, "plain"),
           font.y = c(16, "plain"),
           risk.table.fontsize = 5,
           surv.plot.height = 0.7,
           risk.table.height = 0.3)

svg(filename="tcga_km_DSS_risk.svg", width=4.6, height=6)
tcga_km_DSS_risk
dev.off()


#ACRG cox
ACRG_cox_DSS = coxph(Surv(DSS_time, DSS_status) ~ ACRG_subtype, data = DFSDSS_data)
summary(ACRG_cox_DSS)
pairwise_survdiff(Surv(DSS_time, DSS_status) ~ ACRG_subtype, data = DFSDSS_data)

acrg_km_DSS_risk = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ ACRG_subtype, data = DFSDSS_data), 
           risk.table=TRUE, 
           risk.table.y.text = FALSE, 
           pval= "Logrank test \n p < 0.01", 
           pval.coord = c(80, 0.95),
           palette = c("#A6CEE3", "#3C5488FF", "#8491B4FF", "#33A02C"),
           risk.table.y.text.col = TRUE,
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS probability",
           title = "ACRG Kaplan-Meier",
           legend.title = "ACRG Subtype",
           legend = c(0.30,0.25),
           legend.labs=c("EMT", "MSI", "MSS TP53 Negative", "MSS TP53 Positive"),
           font.legend = c(12, "plain", "black"),
           font.main = c(16, "plain", "black"),
           font.x = c(16, "plain"),
           font.y = c(16, "plain"),
           risk.table.fontsize = 5,
           surv.plot.height = 0.7,
           risk.table.height = 0.3)


svg(filename="acrg_km_DSS_risk.svg", width=4.6, height=6)
acrg_km_DSS_risk
dev.off()

        
DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("Low", "High"))
 
TME_cox_DSS = coxph(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data)
summary(TME_cox_DSS)

tme_km_DSS_risk = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data), 
           risk.table=TRUE, 
           risk.table.y.text = FALSE, 
           pval= "Logrank test \n p < 0.001", 
           pval.coord = c(80,0.25),
           palette = c("#EFC000FF","#925E9FFF"),
           risk.table.y.text.col = TRUE,
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS probability",
           title = "TME Kaplan-Meier",
           legend = c(0.25,0.25),
           legend.title = "TME Subtype",
           legend.labs=c("Low", "High"),
           font.legend = c(12, "plain", "black"),
           font.main = c(16, "plain", "black"),
           font.x = c(16, "plain"),
           font.y = c(16, "plain"),
           risk.table.fontsize = 5,
           surv.plot.height = 0.7,
           risk.table.height = 0.3)

svg(filename="tme_km_DSS_risk.svg", width=4.6, height=6)
tme_km_DSS_risk
dev.off()


```


#Multivariate DSS Cox 

```{r}
#THIS MODEL FOR SUBTYPES ONLY
multivariate_cox = coxph(Surv(DSS_time, DSS_status) ~ STAD_EBV + STAD_MSI + STAD_GS + STAD_CIN + High_cal + Low_cal + MSS_TP53neg + MSS_TP53pos + MSI + EMT, data = DFSDSS_data)
summary(multivariate_cox)
AIC(multivariate_cox)

multivariate_cox_discrete = coxph(Surv(DSS_time, DSS_status) ~ TCGA_subtype + TME_subtype_cal + ACRG_subtype, data = DFSDSS_data)
summary(multivariate_cox_discrete)
wald_mutli = car::Anova(multivariate_cox_discrete)
wald_mutli$adjustp = p.adjust(wald_mutli$`Pr(>Chisq)`, method="BH")

multivariate_cox_table = tbl_regression(multivariate_cox, exponentiate = TRUE)

multivariate_cox_table = as_flex_table(
  multivariate_cox_table,
  include = everything(),
  return_calls = FALSE)
 
flextable::save_as_docx("multivariate_subtypeonly_table_DSS" = multivariate_cox_table,path = "multivariate_subtypeonly_table_DSS.docx")

#####
```
#Multivariate cox forest plot
```{r}
library(forestplot)

#From these models I entered relevant data into .txt file to make forest plot
#############NEW MODELS MARCH 23 2022################################
#####################################################################
multivariate_cox = coxph(Surv(DSS_time, DSS_status) ~ STAD_EBV + STAD_MSI + STAD_GS + STAD_CIN + High_cal + Low_cal + MSS_TP53neg + MSS_TP53pos + MSI + EMT + stage + age+ sex + tumour_location_coarse + study + chemotherapy + radiation, data = DFSDSS_data)
summary(multivariate_cox)

broom <- broom::tidy(multivariate_cox, exponentiate = TRUE, conf.int = TRUE)
broom$compiled = sprintf("%.2f (%.2f, %.2f)", broom$estimate, broom$conf.low, broom$conf.high)
write.csv(broom, "broom_multivariate_survival_DSS_forest.csv")

multivariate_cox_table = tbl_regression(multivariate_cox, exponentiate = TRUE)

multivariate_cox_table = as_flex_table(
  multivariate_cox_table,
  include = everything(),
  return_calls = FALSE)

multivariate_cox_discrete = coxph(Surv(DSS_time, DSS_status) ~ TCGA_subtype + TME_subtype_cal + ACRG_subtype + stage + age+ sex + tumour_location_coarse + study + chemotherapy + radiation, data = DFSDSS_data)
summary(multivariate_cox)
wald_mutli = car::Anova(multivariate_cox_discrete)
wald_mutli$adjustp = p.adjust(wald_mutli$`Pr(>Chisq)`, method="BH")

    
####################################################################
####################################################################
#######################NEW MARCH 15, 2022###########################
####################################################################
####################################################################

#Note: *** < 0.001, ** < 0.01, * <0.05


#Imported table text                 
table_text <- read.delim("~/Documents/R projects/Integrated Gastric Cancer Analyses/multivariate_survival_DSS_forest.txt", header=FALSE)
table_text = as.matrix(table_text)
table_text = na_if(table_text, '')

table_data <- read.delim("~/Documents/R projects/Integrated Gastric Cancer Analyses/multivariate_survival_DSS_forest.txt")

subgps <- c(3,4,5,6,8,9,11,12,13,14,17,18,20,21,23,24,25,26,27,28,29,30,32,33,34)
table_text[subgps] <- paste("  ",table_text[subgps]) 

table_text = as.matrix(table_text[,-c(4:6)])
table_text_list = list(list(), list(), list())
        table_text_list[[1]] <- table_text[,1]
        table_text_list[[2]] <- table_text[,2]
        table_text_list[[3]] <- table_text[,3]
        table_text_list[[1]][15] <- list(expression(bold("Age")))
        table_text_list[[3]][15] <- list(expression(bold("0.13")))
        table_text_list[[1]][1] <- list(expression(bold("Variable")))
        table_text_list[[2]][1] <- list(expression(bold("HR (95% CI)")))
        table_text_list[[1]][2] <- list(expression(bold("TCGA Subtype")))
        table_text_list[[1]][7] <- list(expression(bold("TME Subtype")))
        table_text_list[[1]][10] <- list(expression(bold("ACRG Subtype")))
        table_text_list[[1]][16] <- list(expression(bold("Sex")))
        table_text_list[[1]][19] <- list(expression(bold("Study")))
        table_text_list[[1]][22] <- list(expression(bold("Chemotherapy")))
        table_text_list[[1]][25] <- list(expression(bold("Radiation")))
        table_text_list[[1]][28] <- list(expression(bold("Tumour Location")))
        table_text_list[[1]][31] <- list(expression(bold("Stage")))
        table_text_list[[3]][2] <- list(expression(bold("0.44")))
        table_text_list[[3]][7] <- list(expression(bold("<0.001***")))
        table_text_list[[3]][10] <- list(expression(bold("0.32")))
        table_text_list[[3]][16] <- list(expression(bold("0.22")))
        table_text_list[[3]][19] <- list(expression(bold("0.44")))
        table_text_list[[3]][22] <- list(expression(bold("0.23")))
        table_text_list[[3]][25] <- list(expression(bold("<0.01**")))
        table_text_list[[3]][28] <- list(expression(bold("0.33")))
        table_text_list[[3]][31] <- list(expression(bold("<0.001***")))
        table_text_list[[3]][1] <- list(expression(bold(paste("Wald Test"^"1"))))


forestplot_final = forestplot(table_text_list, mean = cbind(c(NA, table_data$hazard)),lower = cbind(c(NA, table_data$lower)) ,upper = cbind(c(NA, table_data$upper)), 
           new_page = TRUE,
           zero = 1,
           lty.zero = 2,
           lwd.zero = 4,
           col.zero = "black",
           colgap = unit(2,"mm"),
           lineheight = unit(6,"mm"),
           line.margin = unit(0.1,"mm"),
           graphwidth = unit(45,"mm"),
           clip = c(0.1, 6),
           boxsize = 0.6,
           align = c("l", "l", "l"),
           grid = structure((1), gp = gpar(col = "black", lty = 2, lwd = 1)),
           xlog=TRUE,
           vertices = TRUE,
           lwd.ci = 2,
           ci.vertices.height = 0.25,
           xticks = c(0.1, 0.3, 1,2.5,7), 
           col = fpColors(box = "seagreen", lines = "seagreen"),
           txt_gp = fpTxtGp(label = gpar(ps= 7, align ="left", cex = 1.2),
                            ticks = gpar(ps= 7, cex = 1.15),
                            xlab = gpar(ps= 7, cex = 1.15)),
           hrzl_lines = list("2" = gpar(lwd = 1, columns = 1:4, col = "black"), 
                            "35" = gpar(lwd = 1, columns = 1:3, col = "black")),
           xlab  = "Hazard Ratio (95% CI)") |>
  fp_decorate_graph(grid = structure(c(0.1, 0.3,2.5,7),gp = gpar(lty = 2, col = "grey70"))) 
forestplot_final

svg("forestplot_multivar_DSS.svg", width=9, height=9)
forestplot_final
dev.off()



```

#Multivariate cox forest plot chemorads
```{r}
library(forestplot)

DFSDSS_data$chemorads = factor(DFSDSS_data$chemorads, levels = c("No", "Chemorads", "Chemotherapy","Radiotherapy"))
#From these models I entered relevant data into .txt file to make forest plot
#############NEW MODELS MARCH 23 2022################################
#####################################################################
multivariate_cox = coxph(Surv(DSS_time, DSS_status) ~ STAD_EBV + STAD_MSI + STAD_GS + STAD_CIN + High_cal + Low_cal + MSS_TP53neg + MSS_TP53pos + MSI + EMT + stage + age+ sex + tumour_location_coarse + study + chemorads, data = DFSDSS_data)
summary(multivariate_cox)

broom <- broom::tidy(multivariate_cox, exponentiate = TRUE, conf.int = TRUE)
broom$compiled = sprintf("%.2f (%.2f, %.2f)", broom$estimate, broom$conf.low, broom$conf.high)
write.csv(broom, "broom_multivariate_survival_DSS_forest_chemorads.csv")

multivariate_cox_discrete = coxph(Surv(DSS_time, DSS_status) ~ TCGA_subtype + TME_subtype_cal + ACRG_subtype + stage + age+ sex + tumour_location_coarse + study + chemorads, data = DFSDSS_data)
summary(multivariate_cox)
wald_mutli = car::Anova(multivariate_cox_discrete)
wald_mutli$adjustp = p.adjust(wald_mutli$`Pr(>Chisq)`, method="BH")

    
####################################################################
####################################################################
#######################NEW MARCH 15, 2022###########################
####################################################################
####################################################################

#Imported table text                 
table_text <- read.delim("~/Documents/R projects/Integrated Gastric Cancer Analyses/multivariate_survival_DSS_forest_chemorads.txt", header=FALSE)
table_text = as.matrix(table_text)
table_text = na_if(table_text, '')

table_data <- read.delim("~/Documents/R projects/Integrated Gastric Cancer Analyses/multivariate_survival_DSS_forest_chemorads.txt")

subgps <- c(3,4,5,6,8,9,11,12,13,14,17,18,20,21,23,24,25,26,27,28,29,30,31,32,33)
table_text[subgps] <- paste("  ",table_text[subgps]) 

table_text = as.matrix(table_text[,-c(4:6)])
table_text_list = list(list(), list(), list())
        table_text_list[[1]] <- table_text[,1]
        table_text_list[[2]] <- table_text[,2]
        table_text_list[[3]] <- table_text[,3]
        table_text_list[[1]][15] <- list(expression(bold("Age")))
        table_text_list[[3]][15] <- list(expression(bold("0.11")))
        table_text_list[[1]][1] <- list(expression(bold("Variable")))
        table_text_list[[2]][1] <- list(expression(bold("HR (95% CI)")))
        table_text_list[[1]][2] <- list(expression(bold("TCGA Subtype")))
        table_text_list[[1]][7] <- list(expression(bold("TME Subtype")))
        table_text_list[[1]][10] <- list(expression(bold("ACRG Subtype")))
        table_text_list[[1]][16] <- list(expression(bold("Sex")))
        table_text_list[[1]][19] <- list(expression(bold("Study")))
        table_text_list[[1]][22] <- list(expression(bold("Treatment")))
        table_text_list[[1]][27] <- list(expression(bold("Tumour Location")))
        table_text_list[[1]][30] <- list(expression(bold("Stage")))
        table_text_list[[3]][2] <- list(expression(bold("0.46")))
        table_text_list[[3]][7] <- list(expression(bold("<0.001***")))
        table_text_list[[3]][10] <- list(expression(bold("0.34")))
        table_text_list[[3]][16] <- list(expression(bold("0.20")))
        table_text_list[[3]][19] <- list(expression(bold("0.41")))
        table_text_list[[3]][22] <- list(expression(bold("<0.01**")))
        table_text_list[[3]][27] <- list(expression(bold("0.34")))
        table_text_list[[3]][30] <- list(expression(bold("<0.001***")))
        table_text_list[[3]][1] <- list(expression(bold(paste("Wald Test"^"1"))))


forestplot_final = forestplot(table_text_list, mean = cbind(c(NA, table_data$hazard)),lower = cbind(c(NA, table_data$lower)) ,upper = cbind(c(NA, table_data$upper)), 
           new_page = TRUE,
           zero = 1,
           lty.zero = 2,
           lwd.zero = 4,
           col.zero = "black",
           colgap = unit(2,"mm"),
           lineheight = unit(6,"mm"),
           line.margin = unit(0.1,"mm"),
           graphwidth = unit(45,"mm"),
           clip = c(0.1,6),
           boxsize = 0.6,
           align = c("l", "l", "l"),
           grid = structure((1), gp = gpar(col = "black", lty = 2, lwd = 1)),
           xlog=TRUE,
           vertices = TRUE,
           lwd.ci = 2,
           ci.vertices.height = 0.25,
           xticks = c(0.1, 0.3, 1,2.5,7), 
           col = fpColors(box = "seagreen", lines = "seagreen"),
           txt_gp = fpTxtGp(label = gpar(ps= 7, align ="left", cex = 1.2),
                            ticks = gpar(ps= 7, cex = 1.15),
                            xlab = gpar(ps= 7, cex = 1.15)),
           hrzl_lines = list("2" = gpar(lwd = 1, columns = 1:4, col = "black"), 
                            "34" = gpar(lwd = 1, columns = 1:3, col = "black")),
           xlab  = "Hazard Ratio (95% CI)") |>
  fp_decorate_graph(grid = structure(c(0.1, 0.3, 1,2.5,7),gp = gpar(lty = 2, col = "grey70")))
forestplot_final

svg("forestplot_multivar_DSS_chemorads.svg", width=9, height=9)
forestplot_final
dev.off()


```


#****Individual KM curves by TME status
#high vs low for CIN
```{r}
summary(coxph(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$TCGA_subtype=="STAD_CIN",]))

ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$TCGA_subtype=="STAD_CIN",]))

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("High", "Low"))

tme_cin_km = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$TCGA_subtype=="STAD_CIN",]),
           pval= "Logrank test \n p < 0.001", 
           pval.coord = c(0.1, 0.2),
           palette = c("#925E9FFF","#EFC000FF"),
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS Probability",
           title = "CIN-TME Effect",
           legend = "none",
           legend.title = "Molecular subtype",
           legend.labs=c("CIN, TME High", "CIN, TME Low"),
           font.legend = c(12, "plain", "black"),
           font.main = c(14, "plain", "black"),
           surv.plot.height = 0.75)


svg(filename="tme_cin_km_DSS_paper.svg", width=3, height=3)
tme_cin_km
dev.off()

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("Low", "High")) ###CHANGE LEVELS BACK

```
#high vs low for tcga MSI
```{r}
summary(coxph(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$TCGA_subtype=="STAD_MSI",]))

ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$TCGA_subtype=="STAD_MSI",]))

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("High", "Low"))

tme_msi_km = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$TCGA_subtype=="STAD_MSI",]),
           pval= "Logrank test \n p < 0.01", 
           pval.coord = c(0.1, 0.2),
           palette = c("#925E9FFF","#EFC000FF"),
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS Probability",
           title = "TCGA MSI-TME Effect",
           legend = "none",
           legend.title = "Molecular subtype",
           legend.labs=c("MSI, TME High", "MSI, TME Low"),
           font.legend = c(12, "plain", "black"),
           font.main = c(14, "plain", "black"),
           surv.plot.height = 0.75)


svg(filename="tme_tcgamsi_km_DSS_paper.svg", width=3, height=3)
tme_msi_km
dev.off()

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("Low", "High")) ###CHANGE LEVELS BACK

```
#high vs low for EBV
```{r}
summary(coxph(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$TCGA_subtype=="STAD_EBV",]))

ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$TCGA_subtype=="STAD_EBV",]))

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("High", "Low"))

tme_ebv_km = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$TCGA_subtype=="STAD_EBV",]),
           pval= "Logrank test \n p = 0.40", 
           pval.coord = c(0.1, 0.2),
           palette = c("#925E9FFF","#EFC000FF"),
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS Probability",
           title = "EBV-TME Effect",
           legend = "none",
           legend.title = "Molecular subtype",
           legend.labs=c("EBV, TME High", "EBV, TME Low"),
           font.legend = c(12, "plain", "black"),
           font.main = c(14, "plain", "black"),
           surv.plot.height = 0.75)

svg(filename="tme_ebv_km_DSS_paper.svg", width=3, height=3)
tme_ebv_km
dev.off()

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("Low", "High")) ###CHANGE LEVELS BACK

```

#high vs low for acrg MSI
```{r}
summary(coxph(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$ACRG_subtype=="MSI",]))

ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$ACRG_subtype=="MSI",]))

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("High", "Low"))

tme_msi_km = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$ACRG_subtype=="MSI",]),
           pval= "Logrank test \n p < 0.001", 
           pval.coord = c(0.1, 0.2),
           palette = c("#925E9FFF","#EFC000FF"),
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS Probability",
           title = "ACRG MSI-TME Effect",
           legend = "none",
           legend.title = "Molecular subtype",
           legend.labs=c("MSI, TME High", "MSI, TME Low"),
           font.legend = c(12, "plain", "black"),
           font.main = c(14, "plain", "black"),
           surv.plot.height = 0.75) 
           

svg(filename="tme_msi_km_DSS_paper.svg", width=3, height=3)
tme_msi_km
dev.off()

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("Low", "High")) ###CHANGE LEVELS BACK
```

#high vs low for acrg MSS TP53pos
```{r}
summary(coxph(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$ACRG_subtype=="MSS_TP53pos",]))

ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$ACRG_subtype=="MSS_TP53pos",]))

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("High", "Low"))

tme_MSS_TP53pos_km = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$ACRG_subtype=="MSS_TP53pos",]),
           pval= "Logrank test \n p = 0.20", 
           pval.coord = c(0.1, 0.2),
           palette = c("#925E9FFF","#EFC000FF"),
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS Probability",
           title = "MSS TP53+ TME Effect",
           legend = "none",
           legend.title = "Molecular subtype",
           legend.labs=c("MSS TP53+, TME High", "MSS TP53+, TME Low"),
           font.legend = c(12, "plain", "black"),
           font.main = c(14, "plain", "black"),
           surv.plot.height = 0.75) 
           

svg(filename="tme_MSS_TP53pos_km_DSS_paper.svg", width=3, height=3)
tme_MSS_TP53pos_km
dev.off()

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("Low", "High")) ###CHANGE LEVELS BACK
```

#high vs low for acrg MSS TP53neg
```{r}
summary(coxph(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$ACRG_subtype=="MSS_TP53neg",]))

ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$ACRG_subtype=="MSS_TP53neg",]))

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("High", "Low"))

tme_MSS_TP53pos_km = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$ACRG_subtype=="MSS_TP53neg",]),
           pval= "Logrank test \n p < 0.05", 
           pval.coord = c(0.1, 0.2),
           palette = c("#925E9FFF","#EFC000FF"),
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS Probability",
           title = "MSS TP53- TME Effect",
           legend = "none",
           legend.title = "Molecular subtype",
           legend.labs=c("MSS TP53-, TME High", "MSS TP53-, TME Low"),
           font.legend = c(12, "plain", "black"),
           font.main = c(14, "plain", "black"),
           surv.plot.height = 0.75) 
           

svg(filename="tme_MSS_TP53neg_km_DSS_paper.svg", width=3, height=3)
tme_MSS_TP53pos_km
dev.off()

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("Low", "High")) ###CHANGE LEVELS BACK
```

#high vs low for acrg EMT
```{r}
summary(coxph(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$ACRG_subtype=="EMT",]))

ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$ACRG_subtype=="EMT",]))

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("High", "Low"))

tme_emt_km = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$ACRG_subtype=="EMT",]),
           pval= "Logrank test \n p = 0.30", 
           pval.coord = c(0.1, 0.2),
           palette = c("#925E9FFF","#EFC000FF"),
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS Probability",
           title = "ACRG EMT-TME Effect",
           legend = "none",
           legend.title = "Molecular subtype",
           legend.labs=c("EMT, TME High", "EMT, TME Low"),
           font.legend = c(12, "plain", "black"),
           font.main = c(14, "plain", "black"),
           surv.plot.height = 0.75) 
           

svg(filename="tme_emt_km_DSS_paper.svg", width=3, height=3)
tme_emt_km
dev.off()

DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("Low", "High")) ###CHANGE LEVELS BACK
```

#External validation TCGA/ACRG/TME
```{r}
#TCGA cox INTERNAL on TCGA
TCGA_cox_rfs = coxph(Surv(DSS_time, DSS_status) ~ TCGA_subtype, data = DFSDSS_data[DFSDSS_data$study=="TCGA",])
summary(TCGA_cox_rfs)
summary(survfit(Surv(DSS_time, DSS_status) ~ TCGA_subtype, data = DFSDSS_data[DFSDSS_data$study=="TCGA",]), times = 60)
pairwise_survdiff(Surv(DSS_time, DSS_status) ~ TCGA_subtype, data = DFSDSS_data[DFSDSS_data$study=="TCGA",])

tcga_km_DSS_risk = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TCGA_subtype, data = DFSDSS_data[DFSDSS_data$study=="TCGA",]), 
           risk.table=FALSE, 
           risk.table.y.text = FALSE, 
           pval= "Logrank test \n p = 0.2", 
           pval.coord = c(80, 0.95),
           palette = c("#F39B7FFF", "#91D1C2FF", "#4DBBD5FF", "#E64B35FF"),
           risk.table.y.text.col = TRUE,
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS probability",
           legend = c(0.25,0.24),
           title = "TCGA Internal Validation",
           legend.title = "TCGA Subtype",
           legend.labs=c("CIN", "EBV", "GS", "MSI"),
           font.legend = c(14, "plain", "black"),
           font.main = c(16, "plain", "black"),
           font.x = c(16, "plain"),
           font.y = c(16, "plain"),
           risk.table.fontsize = 5,
           surv.plot.height = 0.7,
           risk.table.height = 0.3)

svg(filename="tcga_km_DSS_risk_internal.svg", width=4.6, height=4.6)
tcga_km_DSS_risk
dev.off()

#TCGA cox EXTERNAL on TCGA
TCGA_cox_rfs = coxph(Surv(DSS_time, DSS_status) ~ TCGA_subtype, data = DFSDSS_data[DFSDSS_data$study=="ACRG",])
summary(TCGA_cox_rfs)
summary(survfit(Surv(DSS_time, DSS_status) ~ TCGA_subtype, data = DFSDSS_data[DFSDSS_data$study=="ACRG",]), times = 60)
pairwise_survdiff(Surv(DSS_time, DSS_status) ~ TCGA_subtype, data = DFSDSS_data[DFSDSS_data$study=="ACRG",])

tcga_km_DSS_risk = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TCGA_subtype, data = DFSDSS_data[DFSDSS_data$study=="ACRG",]), 
           risk.table=FALSE, 
           risk.table.y.text = FALSE, 
           pval= "Logrank test \n p = 0.05", 
           pval.coord = c(65, 0.25),
           palette = c("#F39B7FFF", "#91D1C2FF", "#4DBBD5FF", "#E64B35FF"),
           risk.table.y.text.col = TRUE,
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS probability",
           legend = c(0.25,0.24),
           title = "TCGA External Validation",
           legend.title = "TCGA Subtype",
           legend.labs=c("CIN", "EBV", "GS", "MSI"),
           font.legend = c(14, "plain", "black"),
           font.main = c(16, "plain", "black"),
           font.x = c(16, "plain"),
           font.y = c(16, "plain"),
           risk.table.fontsize = 5,
           surv.plot.height = 0.7,
           risk.table.height = 0.3)

svg(filename="tcga_km_DSS_risk_external.svg", width=4.6, height=4.6)
tcga_km_DSS_risk
dev.off()



#ACRG cox Internal on ACRG
ACRG_cox_DSS = coxph(Surv(DSS_time, DSS_status) ~ ACRG_subtype, data = DFSDSS_data[DFSDSS_data$study=="ACRG",])
summary(ACRG_cox_DSS)
pairwise_survdiff(Surv(DSS_time, DSS_status) ~ ACRG_subtype, data = DFSDSS_data[DFSDSS_data$study=="ACRG",])

acrg_km_DSS_risk = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ ACRG_subtype, data = DFSDSS_data[DFSDSS_data$study=="ACRG",]), 
           risk.table=FALSE, 
           risk.table.y.text = FALSE, 
           pval= "Logrank test \n p < 0.05", 
           pval.coord = c(65, 0.95),
           palette = c("#A6CEE3", "#3C5488FF", "#8491B4FF", "#33A02C"),
           risk.table.y.text.col = TRUE,
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS probability",
           title = "ACRG Internal Validation",
           legend.title = "ACRG Subtype",
           legend = c(0.33,0.25),
           legend.labs=c("EMT", "MSI", "MSS TP53 Negative", "MSS TP53 Positive"),
           font.legend = c(14, "plain", "black"),
           font.main = c(16, "plain", "black"),
           font.x = c(16, "plain"),
           font.y = c(16, "plain"),
           risk.table.fontsize = 5,
           surv.plot.height = 0.7,
           risk.table.height = 0.3)


svg(filename="acrg_km_DSS_risk_internal.svg", width=4.6, height=4.6)
acrg_km_DSS_risk
dev.off()


#ACRG cox External on TCGA
ACRG_cox_DSS = coxph(Surv(DSS_time, DSS_status) ~ ACRG_subtype, data = DFSDSS_data[DFSDSS_data$study=="TCGA",])
summary(ACRG_cox_DSS)
pairwise_survdiff(Surv(DSS_time, DSS_status) ~ ACRG_subtype, data = DFSDSS_data[DFSDSS_data$study=="TCGA",])

acrg_km_DSS_risk = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ ACRG_subtype, data = DFSDSS_data[DFSDSS_data$study=="TCGA",]), 
           risk.table=FALSE, 
           risk.table.y.text = FALSE, 
           pval= "Logrank test \n p = 0.5", 
           pval.coord = c(80, 0.95),
           palette = c("#A6CEE3", "#3C5488FF", "#8491B4FF", "#33A02C"),
           risk.table.y.text.col = TRUE,
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS probability",
           title = "ACRG External Validation",
           legend.title = "ACRG Subtype",
           legend = c(0.33,0.198),
           legend.labs=c("EMT", "MSI", "MSS TP53 Negative", "MSS TP53 Positive"),
           font.legend = c(14, "plain", "black"),
           font.main = c(16, "plain", "black"),
           font.x = c(16, "plain"),
           font.y = c(16, "plain"),
           risk.table.fontsize = 5,
           surv.plot.height = 0.7,
           risk.table.height = 0.3)


svg(filename="acrg_km_DSS_risk_external.svg", width=4.6, height=4.6)
acrg_km_DSS_risk
dev.off()

#TME cox Internal on ACRG
DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("Low", "High"))
 
TME_cox_DSS = coxph(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$study=="ACRG",])
summary(TME_cox_DSS)

tme_km_DSS_risk = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$study=="ACRG",]), 
           risk.table=FALSE, 
           risk.table.y.text = FALSE, 
           pval= "Logrank test \n p < 0.001", 
           pval.coord = c(65,0.25),
           palette = c("#EFC000FF","#925E9FFF"),
           risk.table.y.text.col = TRUE,
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS probability",
           title = "TME Internal Validation",
           legend = c(0.25,0.25),
           legend.title = "TME Subtype",
           legend.labs=c("Low", "High"),
           font.legend = c(14, "plain", "black"),
           font.main = c(16, "plain", "black"),
           font.x = c(16, "plain"),
           font.y = c(16, "plain"),
           risk.table.fontsize = 5,
           surv.plot.height = 0.7,
           risk.table.height = 0.3)

svg(filename="tme_km_DSS_risk_internal.svg", width=4.6, height=4.6)
tme_km_DSS_risk
dev.off()


#TME cox External on TCGA
DFSDSS_data$TME_subtype_cal = factor(DFSDSS_data$TME_subtype_cal, levels = c("Low", "High"))
 
TME_cox_DSS = coxph(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$study=="TCGA",])
summary(TME_cox_DSS)

tme_km_DSS_risk = ggsurvplot(survfit(Surv(DSS_time, DSS_status) ~ TME_subtype_cal, data = DFSDSS_data[DFSDSS_data$study=="TCGA",]), 
           risk.table=FALSE, 
           risk.table.y.text = FALSE, 
           pval= "Logrank test \n p < 0.001", 
           pval.coord = c(80,0.25),
           palette = c("#EFC000FF","#925E9FFF"),
           risk.table.y.text.col = TRUE,
           break.time.by = 24,
           xlab = "Time (months)",
           ylab = "DSS probability",
           title = "TME External Validation",
           legend = c(0.25,0.25),
           legend.title = "TME Subtype",
           legend.labs=c("Low", "High"),
           font.legend = c(14, "plain", "black"),
           font.main = c(16, "plain", "black"),
           font.x = c(16, "plain"),
           font.y = c(16, "plain"),
           risk.table.fontsize = 5,
           surv.plot.height = 0.7,
           risk.table.height = 0.3)

svg(filename="tme_km_DSS_risk_external.svg", width=4.6, height=4.6)
tme_km_DSS_risk
dev.off()

```

#Session Info 
R version 4.3.1 (2023-06-16)
Platform: aarch64-apple-darwin20 (64-bit)
Running under: macOS 15.4.1

Matrix products: default
BLAS:   /System/Library/Frameworks/Accelerate.framework/Versions/A/Frameworks/vecLib.framework/Versions/A/libBLAS.dylib 
LAPACK: /Library/Frameworks/R.framework/Versions/4.3-arm64/Resources/lib/libRlapack.dylib;  LAPACK version 3.11.0

locale:
[1] en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8

time zone: America/Vancouver
tzcode source: internal

attached base packages:
[1] grid      stats4    stats     graphics  grDevices utils     datasets  methods   base     

other attached packages:
 [1] ggmosaic_0.3.3        rstatix_0.7.2         tidyr_1.3.1           openxlsx_4.2.8        flextable_0.9.7       gtsummary_2.2.0      
 [7] survey_4.4-2          Matrix_1.6-1.1        forestplot_3.1.6      abind_1.4-8           checkmate_2.3.2       RColorBrewer_1.1-3   
[13] pheatmap_1.0.12       survminer_0.5.0       ggpubr_0.6.0          survival_3.8-3        Rmisc_1.5.1           plyr_1.8.9           
[19] lattice_0.22-7        reshape2_1.4.4        MLmetrics_1.1.3       Metrics_0.1.4         mlr3filters_0.8.1     mlr_2.19.2           
[25] ParamHelpers_1.14.2   remotes_2.5.0         measures_0.3          preprocessCore_1.64.0 stringr_1.5.1         annotate_1.80.0      
[31] XML_3.99-0.18         AnnotationDbi_1.64.1  IRanges_2.36.0        S4Vectors_0.40.2      Biobase_2.62.0        BiocGenerics_0.48.1  
[37] dplyr_1.1.4           devtools_2.4.5        usethis_3.1.0         ggplot2_3.5.2        

loaded via a namespace (and not attached):
  [1] splines_4.3.1           later_1.4.2             palmerpenguins_0.1.1    bitops_1.0-9            tibble_3.2.1            lifecycle_1.0.4        
  [7] globals_0.17.0          backports_1.5.0         magrittr_2.0.3          plotly_4.10.4           rmarkdown_2.29          yaml_2.3.10            
 [13] httpuv_1.6.16           zip_2.3.2               askpass_1.2.1           sessioninfo_1.2.3       pkgbuild_1.4.7          DBI_1.2.3              
 [19] pkgload_1.4.0           zlibbioc_1.48.2         purrr_1.0.4             mlr3misc_0.16.0         RCurl_1.98-1.17         labelled_2.14.0        
 [25] paradox_1.0.1           gdtools_0.4.2           GenomeInfoDbData_1.2.11 KMsurv_0.1-5            ggrepel_0.9.6           listenv_0.9.1          
 [31] cards_0.6.0             cardx_0.2.4             parallelly_1.43.0       svglite_2.1.3           commonmark_1.9.5        codetools_0.2-20       
 [37] ggtext_0.1.2            xml2_1.3.8              tidyselect_1.2.1        farver_2.1.2            broom.helpers_1.20.0    jsonlite_2.0.0         
 [43] ellipsis_0.3.2          Formula_1.2-5           systemfonts_1.2.2       tools_4.3.1             ragg_1.4.0              Rcpp_1.0.14            
 [49] glue_1.8.0              gridExtra_2.3           xfun_0.52               GenomeInfoDb_1.38.8     mlr3_0.23.0             withr_3.0.2            
 [55] fastmap_1.2.0           mitools_2.4             openssl_2.3.2           litedown_0.7            digest_0.6.37           R6_2.6.1               
 [61] mime_0.13               textshaping_1.0.0       colorspace_2.1-1        markdown_2.0            RSQLite_2.3.9           generics_0.1.3         
 [67] fontLiberation_0.1.0    data.table_1.17.0       httr_1.4.7              htmlwidgets_1.6.4       pkgconfig_2.0.3         gtable_0.3.6           
 [73] blob_1.2.4              XVector_0.42.0          survMisc_0.5.6          htmltools_0.5.8.1       fontBitstreamVera_0.1.1 carData_3.0-5          
 [79] profvis_0.4.0           scales_1.3.0            parallelMap_1.5.1       png_0.1-8               lgr_0.4.4               knitr_1.50             
 [85] km.ci_0.5-6             rstudioapi_0.17.1       uuid_1.2-1              cachem_1.1.0            zoo_1.8-14              parallel_4.3.1         
 [91] miniUI_0.1.2            vipor_0.4.7             pillar_1.10.2           vctrs_0.6.5             urlchecker_1.0.1        promises_1.3.2         
 [97] car_3.1-3               xtable_1.8-4            beeswarm_0.4.0          evaluate_1.0.3          BBmisc_1.13             cli_3.6.4              
[103] compiler_4.3.1          rlang_1.1.6             crayon_1.5.3            ggsignif_0.6.4          labeling_0.4.3          forcats_1.0.0          
[109] fs_1.6.6                ggbeeswarm_0.7.2        stringi_1.8.7           viridisLite_0.4.2       munsell_0.5.1           Biostrings_2.70.3      
[115] productplots_0.1.1      lazyeval_0.2.2          fontquiver_0.2.1        hms_1.1.3               bit64_4.6.0-1           future_1.40.0          
[121] KEGGREST_1.42.0         shiny_1.10.0            haven_2.5.4             gridtext_0.1.5          broom_1.0.8             memoise_2.0.1          
[127] fastmatch_1.1-6         bit_4.6.0               officer_0.6.8     
